Comparing gbm vs rf (default parameterisations)

### 2020-10-15 src/s_ar1.Rmd
went back to gbm because of xgbtree poor results in trends

Calculate R* and Rhat across 200 replicates
```{r}
f_replicate <- function(){
  temp <- f_generate_lower_var_four(1/3, 0.3, 1, 2000)
  a_array <- array(dim=c(2000, 4, 1))
  a_array[,,1] <- temp
  a_accuracy <- r_star(a_array, method = "xgbTree")
  mon <- monitor_extra(split_data(a_array))
  return(list(r_star=a_accuracy, r_hat=mon$zfsRhat))
}

@@

Look at predictions of model
```{r}
# add in a column of noise since gbm requires >1 variables
full_data <- f_generate_lower_var_four(1/3, 0.3, 1, 2000) %>% 
  melt() %>% 
  select(-Var1) %>% 
  rename(chain=Var2) %>% 
  mutate(ran_val=rnorm(8000)) %>% 
  mutate(chain=as.factor(chain))
caretGrid <- tibble(nrounds = c(100),
                        max_depth = c(4),
                        eta = c(.4),
                        gamma = 0,
                        colsample_bytree = .7,
                        min_child_weight = 1,
                        subsample = 0.8)

@@

Generate R* distribution based on 2000 iterations for run where chain has lower variance and another where all four chains have same variance
```{r}
temp <- f_generate_lower_var_four(1/3, 0.3, 1, 2000) 
temp1 <- matrix(rnorm(8000), nrow = 2000)
a_array <- array(dim=c(2000, 4, 2))
a_array[,,1] <- temp
a_array[,,2] <- temp1
unmixed <- r_star(a_array, uncertainty = T, method = "xgbTree")

@@

f_replicate_n <- function(n_chains){
  temp <- f_generate_lower_var_n(n_chains, 1/3, 0.3, 1, 2000)
  a_array <- array(dim=c(2000, n_chains, 1))
  a_array[,,1] <- temp
  a_accuracy <- r_star(a_array, method="xgbTree")
  mon <- monitor_extra(split_data(a_array))
  return(list(r_star=a_accuracy, r_hat=mon$zfsRhat))
}

nreplicates <- 50
lnum_chains <- c(2, 4, 6, 8, 16, 32)
mResults <- matrix(nrow = nreplicates * length(lnum_chains),
                   ncol = 4)
k <- 1
for(j in seq_along(lnum_chains)){
  print(j)
  for(i in 1:nreplicates){
    temp <- f_replicate_n(lnum_chains[j])
    mResults[k, ] <- c(lnum_chains[j], i, temp$r_star, temp$r_hat)
    k <- k + 1
  }
}

colnames(mResults) <- c("nchains", "iterate", "R*", "split-Rhat")
mResults <- as.data.frame(mResults) %>% 
  filter(nchains < 64)
saveRDS(mResults, "../data/ar1_numchains.rds")
mResults <- readRDS("../data/ar1_numchains.rds") %>% 
  filter(iterate<=50)
b_sum <- mResults %>% 
  melt(id.vars=c("nchains", "iterate")) %>%
  group_by(nchains, variable) %>% 
  summarise(lower=quantile(value, 0.25),
         upper=quantile(value, 0.75),
         middle=quantile(value, 0.5))

g <- mResults %>% 
  melt(id.vars=c("nchains", "iterate")) %>% 
  left_join(b_sum, by = c("nchains", "variable")) %>% 
  mutate(variable=if_else(variable=="split-Rhat", "Split-Rhat", as.character(variable))) %>% 
  ggplot(aes(x=as.factor(nchains), y=value)) +
  geom_jitter(width = 0.2, colour="grey") +
  geom_pointrange(aes(ymin=lower, y=middle, ymax=upper)) +
  facet_wrap(~variable) +
  scale_x_discrete() +
  xlab("# chains") +
  ylab("Value") +
  scale_color_grey() +
  theme(axis.text = element_text(colour="black", size=16),
        axis.title = element_text(colour="black", size=16),
        strip.text.x = element_text(colour="black", size=16),
        legend.position = "none")
ggsave("../output/ar1_numchains.pdf", g, width = 8, height = 4)

```

@@

lsample_sizes <- c(500, 1000, 2000, 4000, 8000)
nreplicates <- 100
mResults <- matrix(nrow = nreplicates * length(lsample_sizes),
                   ncol = 3)
k <- 1
for(j in seq_along(lsample_sizes)){
  print(j)
  x <- f_generate_lower_var_four(1/3, 0.3, 1, lsample_sizes[j])
  for(i in 1:nreplicates){
    temp <- f_replicate_samplesize(x, lsample_sizes[j])
    mResults[k, ] <- c(lsample_sizes[j], i, temp$r_star)
    k <- k + 1
  }
}

>>>>

Calculate R* and Rhat across 200 replicates
```{r}
f_replicate <- function(){
  temp <- f_generate_lower_var_four(1/4, 0.3, 1, 2000)
  a_array <- array(dim=c(2000, 4, 1))
  a_array[,,1] <- temp
  a_accuracy <- r_star(a_array, method = "xgbTree")
  mon <- monitor_extra(split_data(a_array))
  return(list(r_star=a_accuracy, r_hat=mon$zfsRhat))
}

@@

Look at predictions of model
```{r}
# add in a column of noise since gbm requires >1 variables
full_data <- f_generate_lower_var_four(1/4, 0.3, 1, 2000) %>% 
  melt() %>% 
  select(-Var1) %>% 
  rename(chain=Var2) %>% 
  mutate(ran_val=rnorm(8000)) %>% 
  mutate(chain=as.factor(chain))
caretGrid <- tibble(nrounds = c(100),
                        max_depth = c(4),
                        eta = c(.4),
                        gamma = 0,
                        colsample_bytree = .7,
                        min_child_weight = 1,
                        subsample = 0.8)

@@

Generate R* distribution based on 2000 iterations for run where chain has lower variance and another where all four chains have same variance
```{r}
temp <- f_generate_lower_var_four(1/4, 0.3, 1, 2000) 
temp1 <- matrix(rnorm(8000), nrow = 2000)
a_array <- array(dim=c(2000, 4, 2))
a_array[,,1] <- temp
a_array[,,2] <- temp1
unmixed <- r_star(a_array, uncertainty = T, method = "xgbTree")

@@

f_replicate_n <- function(n_chains){
  temp <- f_generate_lower_var_n(n_chains, 1/4, 0.3, 1, 2000)
  a_array <- array(dim=c(2000, n_chains, 1))
  a_array[,,1] <- temp
  a_accuracy <- r_star(a_array, method="xgbTree")
  mon <- monitor_extra(split_data(a_array))
  return(list(r_star=a_accuracy, r_hat=mon$zfsRhat))
}

nreplicates <- 50
lnum_chains <- c(2, 4, 6, 8, 16, 32, 64)
mResults <- matrix(nrow = nreplicates * length(lnum_chains),
                   ncol = 4)
k <- 1
for(j in seq_along(lnum_chains)){
  print(j)
  for(i in 1:nreplicates){
    temp <- f_replicate_n(lnum_chains[j])
    mResults[k, ] <- c(lnum_chains[j], i, temp$r_star, temp$r_hat)
    k <- k + 1
  }
}

colnames(mResults) <- c("nchains", "iterate", "R*", "split-Rhat")
mResults <- as.data.frame(mResults)
saveRDS(mResults, "../data/ar1_numchains.rds")
mResults <- readRDS("../data/ar1_numchains.rds")
b_sum <- mResults %>% 
  melt(id.vars=c("nchains", "iterate")) %>%
  group_by(nchains, variable) %>% 
  summarise(lower=quantile(value, 0.25),
         upper=quantile(value, 0.75),
         middle=quantile(value, 0.5))

g <- mResults %>% 
  melt(id.vars=c("nchains", "iterate")) %>% 
  left_join(b_sum, by = c("nchains", "variable")) %>% 
  mutate(variable=if_else(variable=="split-Rhat", "Split-Rhat", as.character(variable))) %>% 
  ggplot(aes(x=as.factor(nchains), y=value)) +
  geom_jitter(width = 0.2, colour="grey") +
  geom_pointrange(aes(ymin=lower, y=middle, ymax=upper)) +
  facet_wrap(~variable) +
  scale_x_discrete() +
  xlab("# chains") +
  ylab("Value") +
  scale_color_grey() +
  theme(axis.text = element_text(colour="black", size=16),
        axis.title = element_text(colour="black", size=16),
        strip.text.x = element_text(colour="black", size=16),
        legend.position = "none")
ggsave("../output/ar1_numchains.pdf", g, width = 8, height = 4)
```

@@

lsample_sizes <- c(500, 1000, 2000, 4000, 8000)
nreplicates <- 100
mResults <- matrix(nrow = nreplicates * length(lsample_sizes),
                   ncol = 3)
k <- 1
for(j in seq_along(lsample_sizes)){
  print(j)
  x <- f_generate_lower_var_four(1/4, 0.3, 1, lsample_sizes[j])
  for(i in 1:nreplicates){
    temp <- f_replicate_samplesize(x, lsample_sizes[j])
    mResults[k, ] <- c(lsample_sizes[j], i, temp$r_star)
    k <- k + 1
  }
}

### 2020-10-15 src/s_cauchy.Rmd
went back to gbm because of xgbtree poor results in trends

a_df <- 
  tibble(iteration=iter,
         alt=laccuracy1,
       nom=laccuracy)
saveRDS(a_df, "../output/cauchy_r_star_rf.rds")
```

@@

Add in GBM R*
```{r}
a_df <- readRDS("../output/cauchy_r_star.rds") %>% 
  mutate(model="gbm")
a_df1 <- readRDS("../output/cauchy_r_star_rf.rds") %>% 
  mutate(model="rf")
g2 <- a_df %>%
  bind_rows(a_df1) %>% 
  melt(id.vars=c("iteration", "model")) %>% 
  ggplot(aes(x=iteration, y=value, colour=as.factor(variable), linetype=as.factor(model))) +
  geom_point() +
  geom_line() +
  ylab(TeX("$R^*$")) +
  scale_color_grey("Parameterisation", labels=c("Alternative", "Nominal")) +
  xlab("Iteration") +
  theme(text=element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.83, 0.79),
        legend.text = element_text(size=12, colour="black"),
        legend.title = element_text(size=14, colour="black"),
        axis.title.y = element_blank()) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_x_log10() +
  scale_y_continuous(limits=c(0.8, NA), breaks = seq(1, 7, 1)) +
  ggtitle(TeX("D. Split-$R^*$"))+
  scale_linetype_discrete("Model") +
  guides(colour = guide_legend(nrow = 1, byrow = T),
         linetype=guide_legend(nrow = 1, byrow = T))
ggsave("../output/fig_9d.pdf", g2, width = 12, height = 8)
```

>>>>

a_df <- 
  tibble(iteration=iter,
         alt=laccuracy1,
       nom=laccuracy)
saveRDS(a_df, "../output/cauchy_r_star_rf.rds")

fit <- readRDS("../output/fit_nominal_50000.rds")
x <- rstan::extract(fit, permuted=F, pars="x")

laccuracy <- future_map_dbl(iter, function(i) r_star(x[1:i, , ], method="xgbTree"))

laccuracy1 <- future_map_dbl(iter, function(i) r_star(x[1:i, , ], method="xgbTree"))

a_df <- 
  tibble(iteration=iter,
         alt=laccuracy1,
       nom=laccuracy)
saveRDS(a_df, "../output/cauchy_r_star_xgbtree.rds")
```

@@

Add in GBM R*
```{r}
a_df <- readRDS("../output/cauchy_r_star_xgbtree.rds") %>% 
  mutate(model="gbm")
a_df1 <- readRDS("../output/cauchy_r_star_rf.rds") %>% 
  mutate(model="rf")
g2 <- a_df %>%
  bind_rows(a_df1) %>% 
  melt(id.vars=c("iteration", "model")) %>% 
  ggplot(aes(x=iteration, y=value, colour=as.factor(variable), linetype=as.factor(model))) +
  geom_point() +
  geom_line() +
  ylab(TeX("$R^*$")) +
  scale_color_grey("Parameterisation", labels=c("Alternative", "Nominal")) +
  xlab("Iteration") +
  theme(text=element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.83, 0.79),
        legend.text = element_text(size=12, colour="black"),
        legend.title = element_text(size=14, colour="black"),
        axis.title.y = element_blank()) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_x_log10() +
  scale_y_continuous(limits=c(0.8, NA), breaks = seq(1, 7, 1)) +
  ggtitle(TeX("D. Split-$R^*$"))+
  scale_linetype_discrete("Model") +
  guides(colour = guide_legend(nrow = 1, byrow = T),
         linetype=guide_legend(nrow = 1, byrow = T))
ggsave("../output/fig_9d.pdf", g2, width = 12, height = 8)
```

### 2020-10-15 src/s_eight_schools.Rmd
went back to gbm because of xgbtree poor results in trends

fit_ncp <- sampling(
  model_ncp, data = eight_schools,
  iter = 2000, chains = 4, seed = 483892929, refresh = 0,
  control = list(adapt_delta = 0.95)
)
```

## Break each chain into two then make flattened data
```{r}
# Centered
x <- rstan::extract(fit_cp, permuted=F)
r_star_centered <- r_star_dist(x)
mon_cp <- monitor_extra(split_data(x))

@@

## Look at GBM fitted to data for variable importance
```{r}
caretGrid <- expand.grid(interaction.depth=c(3), n.trees = 50,
                   shrinkage=c(0.1),
                   n.minobsinnode=10)
x <- rstan::extract(fit_cp, permuted=F)
x <- split_data(x)
# Reshape data into form for R* estimation
m_flattened <- matrix(nrow = nrow(x) * 8, ncol = 12)
k <- 1
for(i in 1:8){
  for(j in 1:nrow(x)){
    m_flattened[k, 1:11] <- x[j, i, ]
    m_flattened[k, 12] <- i
    k <- k + 1
  }
}
m_flattened <- m_flattened %>% 
  as.data.frame() %>% 
  rename(chain=V12) %>% 
  mutate(chain=as.factor(chain))

@@

# Fit gradient-boosed model
gbmFit1 <- train(chain ~ ., data = training_data, 
                 method = "gbm",
                 trControl = trainControl(method = 'none'), 
                    tuneGrid = caretGrid, verbose=FALSE)
varImp(gbmFit1)
```

@@

pdf("../output/fig_10.pdf", width = 12, height = 4)
multiplot(g1, g2, g3, cols = 3)
dev.off()
```

>>>>

fit_ncp <- sampling(
  model_ncp, data = eight_schools,
  iter = 2000, chains = 4, seed = 483892929, refresh = 0,
  control = list(adapt_delta = 0.95)
)
```
# Random forest
## Break each chain into two then make flattened data
```{r}
# Centered
x <- rstan::extract(fit_cp, permuted=F)
r_star_centered <- r_star_dist(x)
mon_cp <- monitor_extra(split_data(x))

@@

## Look at GBM fitted to data for variable importance
```{r}
x <- rstan::extract(fit_cp, permuted=F)
x <- split_data(x)
# Reshape data into form for R* estimation
m_flattened <- matrix(nrow = nrow(x) * 8, ncol = 12)
k <- 1
for(i in 1:8){
  for(j in 1:nrow(x)){
    m_flattened[k, 1:11] <- x[j, i, ]
    m_flattened[k, 12] <- i
    k <- k + 1
  }
}
m_flattened <- m_flattened %>% 
  as.data.frame() %>% 
  rename(chain=V12) %>% 
  mutate(chain=as.factor(chain))

@@

# Fit gradient-boosed model
fit <- train(chain ~ ., data = training_data, 
                 method = "rf",
                 trControl = trainControl(method = 'none'), 
                 verbose=FALSE)
varImp(fit)
```

@@

pdf("../output/fig_10.pdf", width = 12, height = 4)
multiplot(g1, g2, g3, cols = 3)
dev.off()
```
# xgbTree

### 2020-10-15 src/s_gbm_vs_rf.Rmd
went back to gbm because of xgbtree poor results in trends

---
title: "Comparing xgbtree vs rf (default parameterisations)"
output: html_notebook
---

@@

f_compare_rf_xgbtree <- function(d, A0, A1){
  lrstar <- vector(length=2)
  ltimes <- vector(length=2)
  x <- f_data_normals(A0, A1, d)
  start <- Sys.time()
  lrstar[1] <- r_star(x, method="rf")
  end <- Sys.time()
  ltimes[1] <- end-start
  start <- Sys.time()
  lrstar[2] <- r_star(x, method="xgbTree")
  end <- Sys.time()
  ltimes[2] <- end-start
  return(list(rstar=lrstar, time=ltimes))
}

f_compare_iter <- function(nreplicate, d, A0, A1){
  m_res <- matrix(nrow=nreplicate, ncol=6)
  for(i in 1:nreplicate){
    temp <- f_compare_rf_xgbtree(d, A0, A1)
    rstars <- temp$rstar
    times <- temp$time
    m_res[i, ] <- c(i, d, rstars[1], rstars[2], times[1], times[2])
  }
  colnames(m_res) <- c("iter", "d", "rstar_rf", "rstar_xgbTree", "time_rf", "time_xgbTree")
  m_res <- m_res %>% 
    as.data.frame()
  return(m_res)
}

nreplicates <- 20
ds <- c(1, 2, 4, 8, 16, 32)
for(i in seq_along(ds)){
  print(i)
  temp_df <- f_compare_iter(nreplicates, ds[i], A0, A1)
  if(i==1)
    big_df <- temp_df
  else
    big_df <- big_df %>% bind_rows(temp_df)
}
saveRDS(big_df, "../data/xgbTree_vs_rf_normals_results.rds")

@@

r_star_opts <- map_dbl(ds[2:length(ds)], ~f_optimal_normals(10000, A0, A1, .))
r_star_opts <- c(1, r_star_opts)
r_star_opts <- tibble(d=ds, optimal=r_star_opts)
temp_df <- 
  big_df %>%
  left_join(r_star_opts) %>% 
  select(-contains("time")) %>% 
  melt(id.vars=c("iter", "d")) %>% 
  group_by(variable, d) %>% 
  summarise(lower=quantile(value, 0.25),
            middle=quantile(value, 0.5),
            upper=quantile(value, 0.75)) %>% 
  ungroup() %>% 
  mutate(variable=as.character(variable)) %>% 
  mutate(variable=if_else(variable=="rstar_rf", "rf", if_else(variable=="rstar_xgbTree", "xgbtree", "optimal")))
saveRDS(temp_df, "../data/xgbTree_vs_rf_normals_results_optimals.rds")
temp_df <- readRDS("../data/xgbTree_vs_rf_normals_results_optimals.rds")
g <- ggplot(data=filter(temp_df, variable!="optimal"),
       aes(x=as.factor(d), y=middle, colour=as.factor(variable))) +
  geom_pointrange(aes(ymin=lower, ymax=upper),
                  position = position_dodge2(width=0.3)) +
  geom_hline(yintercept = 1, linetype=2) +
  geom_point(data=filter(temp_df, variable=="optimal")) +
  scale_color_brewer("Method", palette = "Dark2") +
  xlab("# dimensions") +
  ylab("R*") +
  theme(text = element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"))
ggsave("../output/xgbtree_vs_rf_normal.pdf", g, width = 10, height = 6)
```

@@

f_compare_rf_xgbtree_student_ts <- function(nu1, nu2, d, A0){
  lrstar <- vector(length=2)
  ltimes <- vector(length=2)
  x <- f_data_student_ts(nu1, nu2, d, A0)
  start <- Sys.time()
  lrstar[1] <- r_star(x, method="rf")
  end <- Sys.time()
  ltimes[1] <- end-start
  start <- Sys.time()
  lrstar[2] <- r_star(x, method="xgbTree")
  end <- Sys.time()
  ltimes[2] <- end-start
  return(list(rstar=lrstar, time=ltimes))
}

f_compare_iter_student_t <- function(nreplicate, nu1, nu2, d, A0){
  m_res <- matrix(nrow=nreplicate, ncol=8)
  for(i in 1:nreplicate){
    temp <- f_compare_rf_xgbtree_student_ts(nu1, nu2, d, A0)
    rstars <- temp$rstar
    times <- temp$time
    m_res[i, ] <- c(i, d, nu1, nu2, rstars[1], rstars[2], times[1], times[2])
  }
  colnames(m_res) <- c("iter", "d", "nu1", "nu2", "rstar_rf", "rstar_xgbTree", "time_rf", "time_xgbTree")
  m_res <- m_res %>% 
    as.data.frame()
  return(m_res)
}

@@

for(i in 1:nrow(m_parameters)){
  print(i)
  temp_df <- f_compare_iter_student_t(nreplicates, nu1, m_parameters$nu2[i], m_parameters$ds[i], A0)
  if(i==1)
    big_df <- temp_df
  else
    big_df <- big_df %>% bind_rows(temp_df)
}
saveRDS(big_df, "../data/xgbTree_vs_rf_studentts_results.rds")

@@

r_star_opts <- tibble(d=m_parameters$ds, nu2=m_parameters$nu2, optimal=r_star_opts1)
temp_df <- 
  big_df %>%
  left_join(r_star_opts) %>% 
  select(-contains("time")) %>% 
  select(-one_of("nu1")) %>% 
  melt(id.vars=c("iter", "d", "nu2")) %>% 
  group_by(variable, d, nu2) %>% 
  summarise(lower=quantile(value, 0.25),
            middle=quantile(value, 0.5),
            upper=quantile(value, 0.75)) %>% 
  ungroup() %>% 
  mutate(variable=as.character(variable)) %>% 
  mutate(variable=if_else(variable=="rstar_rf", "rf", if_else(variable=="rstar_xgbTree", "xgbtree", "optimal")))
saveRDS(temp_df, "../data/xgbTree_vs_rf_studentts_results_optimal.rds")
temp_df <- readRDS("../data/xgbTree_vs_rf_studentts_results_optimal.rds")
g2 <- ggplot(data=filter(temp_df, variable!="optimal"),
       aes(x=as.factor(nu2), y=middle, colour=as.factor(variable))) +
  geom_pointrange(aes(ymin=lower, ymax=upper),
                  position = position_dodge2(width=0.3)) +
  geom_hline(yintercept = 1, linetype=2) +
  geom_point(data=filter(temp_df, variable=="optimal")) +
  scale_color_brewer("Method", palette = "Dark2") +
  xlab("# degrees of freedom") +
  ylab("R*") +
  theme(text = element_text(size=16, colour="black"),
        axis.text = element_text(colour="black")) +
  facet_wrap(~d)
ggsave("../output/xgbtree_vs_rf_studentt.pdf", g2, width = 12, height = 8)
```

>>>>

---
title: "Comparing gbm vs rf (default parameterisations)"
output: html_notebook
---

@@

f_compare_rf_gbm <- function(d, A0, A1){
  lrstar <- vector(length=2)
  ltimes <- vector(length=2)
  x <- f_data_normals(A0, A1, d)
  start <- Sys.time()
  lrstar[1] <- r_star(x, method="rf")
  end <- Sys.time()
  ltimes[1] <- end-start
  start <- Sys.time()
  lrstar[2] <- r_star(x, method="gbm")
  end <- Sys.time()
  ltimes[2] <- end-start
  return(list(rstar=lrstar, time=ltimes))
}

f_compare_iter <- function(nreplicate, d, A0, A1){
  m_res <- matrix(nrow=nreplicate, ncol=6)
  for(i in 1:nreplicate){
    temp <- f_compare_rf_gbm(d, A0, A1)
    rstars <- temp$rstar
    times <- temp$time
    m_res[i, ] <- c(i, d, rstars[1], rstars[2], times[1], times[2])
  }
  colnames(m_res) <- c("iter", "d", "rstar_rf", "rstar_gbm", "time_rf", "time_gbm")
  m_res <- m_res %>% 
    as.data.frame()
  return(m_res)
}

nreplicates <- 20
ds <- c(1, 2, 4, 8, 16, 32)
for(i in seq_along(ds)){
  print(i)
  temp_df <- f_compare_iter(nreplicates, ds[i], A0, A1)
  if(i==1)
    big_df <- temp_df
  else
    big_df <- big_df %>% bind_rows(temp_df)
}
saveRDS(big_df, "../data/gbm_vs_rf_normals_results.rds")

@@

r_star_opts <- map_dbl(ds[2:length(ds)], ~f_optimal_normals(10000, A0, A1, .))
r_star_opts <- c(1, r_star_opts)
r_star_opts <- tibble(d=ds, optimal=r_star_opts)
temp_df <- 
  big_df %>%
  left_join(r_star_opts) %>% 
  select(-contains("time")) %>% 
  melt(id.vars=c("iter", "d")) %>% 
  group_by(variable, d) %>% 
  summarise(lower=quantile(value, 0.25),
            middle=quantile(value, 0.5),
            upper=quantile(value, 0.75)) %>% 
  ungroup() %>% 
  mutate(variable=as.character(variable)) %>% 
  mutate(variable=if_else(variable=="rstar_rf", "rf", if_else(variable=="rstar_gbm", "gbm", "optimal")))
saveRDS(temp_df, "../data/gbm_vs_rf_normals_results_optimals.rds")
temp_df <- readRDS("../data/gbm_vs_rf_normals_results_optimals.rds")
g <- ggplot(data=filter(temp_df, variable!="optimal"),
       aes(x=as.factor(d), y=middle, colour=as.factor(variable))) +
  geom_pointrange(aes(ymin=lower, ymax=upper),
                  position = position_dodge2(width=0.3)) +
  geom_hline(yintercept = 1, linetype=2) +
  geom_point(data=filter(temp_df, variable=="optimal")) +
  scale_color_brewer("Method", palette = "Dark2") +
  xlab("# dimensions") +
  ylab("R*") +
  theme(text = element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"))
ggsave("../output/gbm_vs_rf_normal.pdf", g, width = 10, height = 6)
```

@@

f_compare_rf_gbm_student_ts <- function(nu1, nu2, d, A0){
  lrstar <- vector(length=2)
  ltimes <- vector(length=2)
  x <- f_data_student_ts(nu1, nu2, d, A0)
  start <- Sys.time()
  lrstar[1] <- r_star(x, method="rf")
  end <- Sys.time()
  ltimes[1] <- end-start
  start <- Sys.time()
  lrstar[2] <- r_star(x, method="gbm")
  end <- Sys.time()
  ltimes[2] <- end-start
  return(list(rstar=lrstar, time=ltimes))
}

f_compare_iter_student_t <- function(nreplicate, nu1, nu2, d, A0){
  m_res <- matrix(nrow=nreplicate, ncol=8)
  for(i in 1:nreplicate){
    temp <- f_compare_rf_gbm_student_ts(nu1, nu2, d, A0)
    rstars <- temp$rstar
    times <- temp$time
    m_res[i, ] <- c(i, d, nu1, nu2, rstars[1], rstars[2], times[1], times[2])
  }
  colnames(m_res) <- c("iter", "d", "nu1", "nu2", "rstar_rf", "rstar_gbm", "time_rf", "time_gbm")
  m_res <- m_res %>% 
    as.data.frame()
  return(m_res)
}

@@

for(i in 1:nrow(m_parameters)){
  print(i)
  temp_df <- f_compare_iter_student_t(nreplicates, nu1, m_parameters$nu2[i], m_parameters$ds[i], A0)
  if(i==1)
    big_df <- temp_df
  else
    big_df <- big_df %>% bind_rows(temp_df)
}
saveRDS(big_df, "../data/gbm_vs_rf_studentts_results.rds")

@@

r_star_opts <- tibble(d=m_parameters$ds, nu2=m_parameters$nu2, optimal=r_star_opts1)
temp_df <- 
  big_df %>%
  left_join(r_star_opts) %>% 
  select(-contains("time")) %>% 
  select(-one_of("nu1")) %>% 
  melt(id.vars=c("iter", "d", "nu2")) %>% 
  group_by(variable, d, nu2) %>% 
  summarise(lower=quantile(value, 0.25),
            middle=quantile(value, 0.5),
            upper=quantile(value, 0.75)) %>% 
  ungroup() %>% 
  mutate(variable=as.character(variable)) %>% 
  mutate(variable=if_else(variable=="rstar_rf", "rf", if_else(variable=="rstar_gbm", "gbm", "optimal")))
saveRDS(temp_df, "../data/gbm_vs_rf_studentts_results_optimal.rds")
temp_df <- readRDS("../data/gbm_vs_rf_studentts_results_optimal.rds")
g2 <- ggplot(data=filter(temp_df, variable!="optimal"),
       aes(x=as.factor(nu2), y=middle, colour=as.factor(variable))) +
  geom_pointrange(aes(ymin=lower, ymax=upper),
                  position = position_dodge2(width=0.3)) +
  geom_hline(yintercept = 1, linetype=2) +
  geom_point(data=filter(temp_df, variable=="optimal")) +
  scale_color_brewer("Method", palette = "Dark2") +
  xlab("# degrees of freedom") +
  ylab("R*") +
  theme(text = element_text(size=16, colour="black"),
        axis.text = element_text(colour="black")) +
  facet_wrap(~d)
ggsave("../output/gbm_vs_rf_studentt.pdf", g2, width = 12, height = 8)
```
